---
title: "Strategy - boundSkew2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
library(Hmisc)
source('../05_graph_strategy.R')
```

All items are a Likert scale:  
1 - Strongly disagree  
2 - Somewhat disagree  
3 - Neutral  
4 - Somewhat agree  
5 - Strongly agree  

## Group Means
``` {r means, echo = FALSE}
means
```

#### - More people used a mathematical strategy compared to going with their gut.
```{r compare general, echo = FALSE, comment = ''}
gutvmath
```

#### - People were more likely to focus om winning compared to losing.
#### - People were more likely to focus on the monetary amount instead of the likelihood of winning or losing.
#### - No interaction between valence (win vs loss) and parameter (magnitude or probability)
```{r compare info, echo = FALSE, comment = ''}
summary(valvparam)
```

## General Strategies

### "I tried to solve the task on a gut level."
```{r Gut, echo = FALSE, warning=FALSE} 
gut_color <- colorize_variable(d0$gut)
p1 <- ggplot(d0, aes(Age, gut))
p2 <- ggplot(d0, aes(gut, fill = gut_color))
fancy_graph(p1,p2, gut_color, 'Gut Feeling')
```

#### Age: _r_ = `r round(rcorr(d0$Age, d0$gut)$r[2],3) `, _p_ = `r round(rcorr(d0$Age, d0$gut)$P[2], 3)`

### "I tried to solve the task mathematically."
```{r Math, echo = FALSE, warning=FALSE} 
math_color <- colorize_variable(d0$math)
p1 <- ggplot(d0, aes(Age, math))
p2 <- ggplot(d0, aes(math, fill = math_color))
fancy_graph(p1,p2, math_color, 'Mathematically')
```

#### Age: _r_ = `r round(rcorr(d0$Age, d0$math)$r[2],3) `, _p_ = `r round(rcorr(d0$Age, d0$math)$P[2], 3)`

## Information Strategies

### "I tried to solve the task by focusing on how much money I could win."
```{r money win, echo = FALSE, warning=FALSE} 
win.money_color <- colorize_variable(d0$win.money)
p1 <- ggplot(d0, aes(Age, win.money))
p2 <- ggplot(d0, aes(win.money, fill = win.money_color))
fancy_graph(p1,p2, win.money_color, 'Win Money')
```

#### Age: _r_ = `r round(rcorr(d0$Age, d0$win.money)$r[2],3) `, _p_ = `r round(rcorr(d0$Age, d0$win.money)$P[2], 3)`

### "I tried to solve the task by focusing on how much money I could lose."
```{r money lose, echo = FALSE, warning=FALSE} 
lose.money_color <- colorize_variable(d0$lose.money)
p1 <- ggplot(d0, aes(Age, lose.money))
p2 <- ggplot(d0, aes(lose.money, fill = lose.money_color))
fancy_graph(p1,p2, lose.money_color, 'Lose Money')
```

#### Age: _r_ = `r round(rcorr(d0$Age, d0$lose.money)$r[2],3) `, _p_ = `r round(rcorr(d0$Age, d0$lose.money)$P[2], 3)`

### "I tried to solve the task by focusing on how likely it was that I would win."
```{r win likely, echo = FALSE, warning=FALSE} 
win.likely_color <- colorize_variable(d0$win.likely)
p1 <- ggplot(d0, aes(Age, win.likely))
p2 <- ggplot(d0, aes(win.likely, fill = win.likely_color))
fancy_graph(p1,p2, win.likely_color, 'Win Likely')
```

#### Age: _r_ = `r round(rcorr(d0$Age, d0$win.likely)$r[2],3) `, _p_ = `r round(rcorr(d0$Age, d0$win.likely)$P[2], 3)`

### "I tried to solve the task by focusing on how likely it was that I would lose."
```{r lose likely, echo = FALSE, warning=FALSE} 
lose.likely_color <- colorize_variable(d0$lose.likely)
p1 <- ggplot(d0, aes(Age, lose.likely))
p2 <- ggplot(d0, aes(lose.likely, fill = lose.likely_color))
fancy_graph(p1,p2, lose.likely_color, 'Lose Likely')
```

#### Age: _r_ = `r round(rcorr(d0$Age, d0$lose.likely)$r[2],3) `, _p_ = `r round(rcorr(d0$Age, d0$lose.likely)$P[2], 3)`

## Gut v Money by Age
```{r, echo = FALSE}
ggplot(d0, aes(Age, diffstrategy)) + geom_point() + geom_smooth(method = 'lm', fill = 'Blue') +
  geom_smooth(method = "lm", formula = y ~ x + I(x^2), color = 'Red', fill = 'Red') 
```

#### Age: _r_ = `r round(rcorr(d0$Age, d0$diffstrategy)$r[2],3) `, _p_ = `r round(rcorr(d0$Age, d0$diffstrategy)$P[2], 3)`