---
title: "05_Cognitive"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
library(Hmisc)
source('../07_graph_cognitive.R')
```

## Subjective Graph Literacy

```{r sgl frequency, echo = FALSE}
sgl1
```

#### SGL scores ranged from `r range(d1$graph_lit)[1]` to `r range(d1$graph_lit)[2]` with an average score of `r round(mean(d1$graph_lit))` (red dotted line).

```{r sgl age, echo = FALSE}
sgl2
```

#### There was no significant relationship between age and graph literacy, _r_ = `r round(rcorr(d1$Age, d1$graph_lit)$r[2], 3)`, _p_ = `r round(rcorr(d1$Age, d1$graph_lit)$P[2], 3)`  

## Numeracy
```{r num frequency, echo = FALSE}
num1
```

#### Numeracy scores ranged from `r range(d3$Numeracy)[1]` to `r range(d3$Numeracy)[2]` with an average score of `r round(mean(d3$Numeracy))` (red dotted line).

```{r num age, echo = FALSE}
num2
```

#### There was a significant increase in numeracy with age, _r_ = `r round(rcorr(d3$Age, d3$Numeracy)$r[2], 3)`, _p_ = `r round(rcorr(d3$Age, d3$Numeracy)$P[2], 3)`. 
