---
title: "Real World - boundSkew2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
library(Hmisc)
source('../08_graph_real_world.R')
```

## Investments

``` {r invest1, echo = FALSE}
invest1
```

### Most participants (_N_ = `r n_lost_invest` / `r n_total`) have lost money in an investment, but ...

``` {r why loss, echo = FALSE}
invest2
```

### only a small proportion (_N_ = `r n_fraud` / `r n_lost_invest`) attribute this to fraud.

## Susceptibility to Fraud

### While most people are ambivalent about their ability to detect fraud, 

``` {r detect, echo = FALSE}
fraud1
```

### most are confident that they can avoid fraudulent investments

``` {r fraud, echo = FALSE}
fraud2
```

### and resist high-pressure sales tactics.

``` {r pressure, echo = FALSE}
fraud3
```

## Age effects

### "How able are you to detect a fraudulent investment?"
```{r detect age, echo = FALSE, warning=FALSE} 
detect_color <- colorize_variable7(d3$detect_fraud)
p1 <- ggplot(d3, aes(Age, detect_fraud)) + geom_point()
p2 <- ggplot(d3, aes(detect_fraud, fill = detect_color))
fancy_graph(p1,p2, detect_color, 'Detect Fraud Investment')
```

#### Age: _r_ = `r round(rcorr(d3$Age, d3$detect_fraud)$r[2],3) `, _p_ = `r round(rcorr(d3$Age, d3$detect_fraud)$P[2], 3)`

### "How likely are you to make a fraudulent investment?"
```{r likely age, echo = FALSE, warning=FALSE} 
likely_color <- colorize_variable7(d3$likely_fraud)
p1 <- ggplot(d3, aes(Age, likely_fraud)) + geom_point()
p2 <- ggplot(d3, aes(likely_fraud, fill = likely_color))
fancy_graph(p1,p2, likely_color, 'Likely to make  Fraud Investment')
```

#### Age: _r_ = `r round(rcorr(d3$Age, d3$likely_fraud)$r[2],3) `, _p_ = `r round(rcorr(d3$Age, d3$likely_fraud)$P[2], 3)`

### How able are you to resist high-pressure sales tactics when buying investments?"
```{r high pressure age, echo = FALSE, warning=FALSE} 
hp_color <- colorize_variable7(d3$high_pressure)
p1 <- ggplot(d3, aes(Age, high_pressure)) + geom_point()
p2 <- ggplot(d3, aes(high_pressure, fill = hp_color))
fancy_graph(p1,p2, hp_color, 'Resist High Pressure Sales')
```

#### Age: _r_ = `r round(rcorr(d3$Age, d3$high_pressure)$r[2],3) `, _p_ = `r round(rcorr(d3$Age, d3$high_pressure)$P[2], 3)`
